Patient movements

### 2024-03-04 analysis/environmental-data.Rmd
Update plots

```{r}
co2_pl <- cont_df %>%
  mutate(time = floor_date(time, "10 minutes")) %>%
  group_by(mthdy, time, room) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = co2, color = mthdy)) +
  geom_step() +
  facet_wrap(~room) +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "4 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = expression("CO"[2] * " (parts per million, ppm)"),
    title = "a"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    panel.spacing = unit(1, "lines"),
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

@@

```{r}
aer_pl <- aer %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = room, fill = room, y = aer)) +
  geom_boxplot() +
  # geom_jitter(
  #   mapping = aes(color = daytime),
  #   width = 0.2,
  #   height = 0,
  #   shape = 21
  # ) +
  scale_fill_manual(values = wes_palette("Royal2")[-1]) +
  scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, NA)) +
  labs(
    y = "Air changes per hour",
    title = "b"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.95)
  ) +
  guides(fill = "none")

>>>>

```{r}
co2_pl <- cont_df %>%
  mutate(time = floor_date(time, "10 minutes")) %>%
  group_by(mthdy, time, room) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = co2, color = mthdy)) +
  geom_step() +
  facet_wrap(~room) +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "4 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = expression("CO"[2] * " (parts per million, ppm)"),
    title = "f"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    panel.spacing = unit(1, "lines"),
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

@@

```{r}
aer %>%
  group_by(room) %>%
  tidybayes::median_qi(aer, .width = .5) %>%
  mutate_if(is.numeric, round)

aer_pl <- aer %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = room, fill = room, y = aer)) +
  geom_boxplot() +
  # geom_jitter(
  #   mapping = aes(color = daytime),
  #   width = 0.2,
  #   height = 0,
  #   shape = 21
  # ) +
  scale_fill_manual(values = wes_palette("Royal2")[-1]) +
  scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, NA)) +
  labs(
    y = "Air changes per hour",
    title = "g"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.95)
  ) +
  guides(fill = "none")

### 2024-03-04 analysis/patient-tracking.Rmd
Update plots

time_in_clin_pl <- time_in_clin %>%
  filter(tracking_end != "Possible HCW") %>%
  dplyr::select(-tracking_end) %>%
  melt(c("date", "patient_id")) %>%
  mutate(variable = factor(
    variable,
    levels = c("Clinic", "Waiting room", "TB room", "Corridor")
  )) %>%
  ggplot(aes(x = variable, fill = variable, y = value)) +
  geom_boxplot() +
  scale_y_sqrt(breaks = c(0, 1, 10, 30, 60, 120, 180)) +
  scale_fill_manual(values = wes_palette("Royal2")) +
  labs(
    y = "Time in clinic (min)",
    title = "e"
  ) +
  theme_custom(8) +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title.position = "plot"
  )

@@

@@

cc_n_pl <- close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = n_cc)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    y = "Density", x = "Number of close contacts",
    title = "f"
    # subtitle = "Defined as <1m for >1min"
  ) +
  geom_density(fill = "grey70", color = "grey0", alpha = 0.8) +
  theme_custom(8) +
  theme(
    plot.title.position = "plot",
    plot.margin = margin(r = 11),
    plot.subtitle = element_text(margin = margin(b = 11))
  )

@@

cc_t_pl <- close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = cc_time / Clinic * 100)) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 100)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    y = "Density",
    x = "Time in close contact (%)",
    title = "g"
  ) +
  geom_density(
    fill = "grey70", color = "grey0", alpha = 0.8
  ) +
  theme_custom(8) +
  theme(
    plot.title.position = "plot",
    plot.margin = margin(r = 11)
  )

@@

time_pl <- clinic_occupancy %>%
  filter(variable == "Clinic") %>%
  ggplot(aes(x = time, y = value, color = date)) +
  geom_step() +
  # ggh4x::facet_wrap2(~variable, axes = "x", remove_labels = "all") +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "3 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = "Number of people in clinic",
    title = "d"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

@@

```{r}
spatial_pl <- plot_spatial(
  ggplot(data = df, mapping = aes(x = x, y = y)) +
    geom_bin2d(binwidth = 200),
  text_descr = 8
) +
  labs(
    fill = "Number of tracks",
    title = "c"
  ) +
  scale_fill_gradientn(
    colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
    trans = "log10",
    labels = scales::comma,
    breaks = c(1, 10, 100, 1000, 10000)
  ) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.height = unit(0.2, "cm"),
    legend.key.width = unit(1, "cm")
  ) +
  guides(fill = guide_colorbar(title.vjust = 1))

>>>>

time_in_clin %>%
  filter(tracking_end != "Possible HCW") %>%
  tidybayes::median_qi(`Clinic`, .width = .5) %>%
  mutate_if(is.numeric, round)

time_in_clin_pl <- time_in_clin %>%
  filter(tracking_end != "Possible HCW") %>%
  dplyr::select(-tracking_end) %>%
  melt(c("date", "patient_id")) %>%
  mutate(variable = factor(
    variable,
    levels = c("Clinic", "Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = variable, fill = variable, y = value)) +
  geom_boxplot() +
  scale_y_sqrt(breaks = c(0, 1, 10, 30, 60, 120, 180)) +
  scale_fill_manual(values = wes_palette("Royal2")) +
  labs(
    y = "Time in clinic (min)",
    title = "c"
  ) +
  theme_custom(8) +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title.position = "plot"
  )

@@

no_close_contacts %>%
  filter(tracking_end != "Possible HCW") %>%
  tidybayes::median_qi(n_cc, .width = .5) %>%
  mutate_if(is.numeric, round)

@@

cc_n_pl <- close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = n_cc)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    y = "Density", x = "Number of close contacts",
    title = "d"
    # subtitle = "Defined as <1m for >1min"
  ) +
  geom_density(fill = "grey70", color = "grey0", alpha = 0.8) +
  theme_custom(8) +
  theme(
    plot.title.position = "plot",
    plot.margin = margin(r = 11),
    plot.subtitle = element_text(margin = margin(b = 11))
  )

@@

close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  tidybayes::median_qi(cc_time / Clinic * 100, .width = .5) %>%
  mutate_if(is.numeric, round)

cc_t_pl <- close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = cc_time / Clinic * 100)) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 100)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    y = "Density",
    x = "Time in close contact (%)",
    title = "e"
  ) +
  geom_density(
    fill = "grey70", color = "grey0", alpha = 0.8
  ) +
  theme_custom(8) +
  theme(
    plot.title.position = "plot",
    plot.margin = margin(r = 11)
  )

@@

time_pl <- clinic_occupancy %>%
  filter(variable == "Clinic") %>%
  ggplot(aes(x = time, y = value, color = date)) +
  geom_step() +
  # ggh4x::facet_wrap2(~variable, axes = "x", remove_labels = "all") +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "3 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = "Number of tracks",
    title = "b"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

@@

```{r}
spatial_pl <- plot_spatial(
  ggplot(data = df, mapping = aes(x = x, y = y)) +
    geom_bin2d(binwidth = 200),
  text_descr = 8
) +
  labs(
    fill = "Number of tracks",
    title = "a"
  ) +
  scale_fill_gradientn(
    colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
    trans = "log10",
    labels = scales::comma,
    breaks = c(1, 10, 100, 1000, 10000)
  ) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.height = unit(0.2, "cm"),
    legend.key.width = unit(1, "cm")
  ) +
  guides(fill = guide_colorbar(title.vjust = 1))
